# Regressões

## polynomial

```{r}
data("phao")
with(phao, polynomial(dose,comp, grau = 2))
```

## polynomial2

```{r}
dose=rep(c(0,0,0,2,2,2,4,4,4,6,6,6),3)
resp=c(8,7,5,23,24,25,30,34,36,80,90,80,12,14,15,23,24,25,50,54,56,80,90,40,
12,14,15,3,4,5,50,54,56,80,90,40)
trat=rep(c("A","B","C"),e=12)
polynomial2(dose, resp, trat, grau=c(1,2,3))
```

## polynomial2_color

```{r}
polynomial2_color(dose, resp, trat, grau=c(1,2,3))
```

# Teste de Dunnett

## DIC

```{r}
data("pomegranate")
with(pomegranate,dunnett(trat=trat,resp=WL,control="T1"))
```

## Esquema fatorial

```{r}
data(cloro)
attach(cloro)
respAd=c(268, 322, 275, 350, 320)
data=rbind(data.frame(trat=paste(f1,f2,sep = ""),bloco=bloco,resp=cloro$resp),
           data.frame(trat=c("Test","Test","Test","Test","Test"),
                      bloco=unique(bloco),resp=respAd))
with(data,dunnett(trat = trat,
                  resp = resp,
                  control = "Test",
                  block=bloco,model = "DBC"))
```


# Gráficos externos

```{r,fig.show='hide',message=FALSE,results='hide'}
data(pomegranate)
graph=with(pomegranate,DIC(trat,WL,mcomp = "sk"))
```

## barplot_positive

```{r}
barplot_positive(graph,graph)
```

## bar_graph

```{r}
bar_graph(graph)
```

```{r}
bar_graph(graph,horiz = FALSE)
```

## seg_graph

```{r}
seg_graph(graph)
```
```{r}
seg_graph(graph,horiz = FALSE)
```

## plot_jitter

```{r}
plot_jitter(graph)
```

## sk_graph

```{r}
sk_graph(graph)
```

## radargraph

```{r}
radargraph(graph)
```
## plot_interaction

```{r,results='hide',message=FALSE,fig.show='hide'}
data(cloro)
a=with(cloro, FAT2DIC(f1, f2, resp))
```

```{r}
plot_interaction(a)
```

# Correlação

## corgraph

```{r}
data("pomegranate")
corgraph(pomegranate[,-1])
```

## cor_ic

```{r}
data("pomegranate")
cor_ic(pomegranate[,-1])
```

## plot_cor

```{r}
data("pomegranate")
with(pomegranate, plot_cor(WL, SS, xlab="WL", ylab="SS"))
```

# Gráfico temperatura/umidade

## plot_TH

```{r}
data(weather)
with(weather, plot_TH(tempo, Tmed, Tmax, Tmin, UR))
```

## plot_TH1

```{r}
data(weather)
with(weather, plot_TH1(tempo, Tmed, Tmax, Tmin, UR))
```

# Gráfico radar/aranha

```{r}
data(sensorial)
with(sensorial, spider_graph(resp, variable, Blend))
```

# Gráfico de linhas descritivo

```{r}
dose=rep(c(0,2,4,6,8,10),e=3,2)
resp=c(seq(1,18,1),seq(2,19,1))
fator=rep(c("A","B"),e=18)
line_plot(dose,resp,fator)
```

# Área abaixo da curva

```{r}
data("simulate1")

# Converting to readable format for function
dados=cbind(simulate1[simulate1$tempo==1,3],
            simulate1[simulate1$tempo==2,3],
            simulate1[simulate1$tempo==3,3],
            simulate1[simulate1$tempo==4,3],
            simulate1[simulate1$tempo==5,3],
            simulate1[simulate1$tempo==6,3])
colnames(dados)=c(1,2,3,4,5,6)
dados
```


```{r}
resp=aacp(dados)
trat=simulate1$trat[simulate1$tempo==1]
# Analyzing by DIC function
DIC(trat,resp)
```

# Referências

 - Principles and procedures of statistics a biometrical approach Steel, Torry and Dickey. Third Edition 1997

 - Multiple comparisons theory and methods. Departament of statistics the Ohio State University. USA, 1996. Jason C. Hsu. Chapman Hall/CRC.

 - Practical Nonparametrics Statistics. W.J. Conover, 1999

 - Ramalho M.A.P., Ferreira D.F., Oliveira A.C. 2000. Experimentacao em Genetica e Melhoramento de Plantas. Editora UFLA.

 - Scott R.J., Knott M. 1974. A cluster analysis method for grouping mans in the analysis of variance. Biometrics, 30, 507-512.

 - Mendiburu, F., and de Mendiburu, M. F. (2019). Package ‘agricolae’. R Package, Version, 1-2.
 
 - Wobbrock, J. O., Findlater, L., Gergle, D., Higgins, J. J. (2011, May). The aligned rank transform for nonparametric factorial analyses using only anova procedures. In Proceedings of the SIGCHI conference on human factors in computing systems (pp. 143-146).

 - Kay, M., Wobbrock, J. O. (2020). Package ‘ARTool’.
 
 - Seber, G. A. F. and Wild, C. J (1989) Nonlinear Regression, New York: Wiley \& Sons (p. 330).

 - Ritz, C.; Strebig, J.C.; Ritz, M.C. Package ‘drc’. Creative Commons: Mountain View, CA, USA, 2016.
